Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage

### 2022-08-25 paper/paper.tex
UAV simulation Fa,Fs

\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

@@

\begin{abstract}
In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage. The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them. Then we focus on two issues, local motion planning and tracking control. We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot. The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail. By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation. The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure. Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved. Simulations are given ...
\end{abstract}

\begin{keywords}
biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, search and rescue, smoothing signal model, UAV, UAVs-UGVs team system
\end{keywords}

@@

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as search and rescue, battlefield, logistics and transportation, and surveillance, etc (cite:UV). Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}. However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS). Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.

@@

Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV). Additionally, the complementarity between them also makes such a system more potential. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAVs-UGVs team system will be more appealing. To discuss more concretely, we consider an UAVs-UGVs team system for search and rescue. For the need for search mobility, we choose quadrotor aircraft as UAV. In order to deal with the complex terrain of the search and rescue environment, we choose biped robot as UGV. Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent search and rescue system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose an system architecture of UAVs-robots team system (URTS) for search and rescue usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control. It is because the UTRS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a target location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to determine. Then, a local motion corresponding to the behavior of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

% To discuss the local motion planning problem and tracking control problem, the real mechanical system for each agent corresponds must be considered. To meet the need for search mobility, we choose quadrotor aircraft as UAV. The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control). In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV. Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system. However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved. The local motion planning of the walking of biped robot, i.e., stable walking pattern generation, is discussed in this paper. Related researches can be found in (cite: walking pattern).

@@

\section{PRELIMINARIES OF search and rescue URTS}
The URTS will start with a given search and rescue area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$. The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall search area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target. 
% It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

@@

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=.5]{fig/sys.pdf}\caption{The system architecture of agent in URTS. The 2 blocks on left side are used to convert low-level sensor information into high-level information, such as map, start point and object information. The 5 blocks on right side are the flow of an agent performing a search and rescue mission. From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control}%
\label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

@@

\subsection{motion planning of flying of UAV}
A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f \\ \tau
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % form 2
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust. This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction. Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. $(\sigma_n')$ is the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS. Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command. In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}). Therefore, through appropriate conversion, the above disturbances can be equivalent to an disturbance force $d_1(t)$. The nominal system (\ref{eq:agent}) then be rewrited as the following real system:

@@

where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))$ is the unknown actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.

@@

where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference. The derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed. For the convenience of analysis, let us choose $Z_0=\{ 0,1,\dots,p-1 \}$. By changing index $k$ to $j$, the derivative of $f_i(t-jh),j\in{Z_0}$ can be obtained by (\ref{eq:df}):
\begin{equation} \label{eq:df1}
    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t)
where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
    \dot{F}_i(t)=A_iF_i(t)+v_i(t)
where $v_i(t)=\begin{bmatrix}
    \epsilon_0^T(t) & \epsilon_1^T(t) & \dots & \epsilon_{p-1}^T(t)
\end{bmatrix}^T$, $F_i(t)=\begin{bmatrix}
    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:smooth model})
\begin{equation} \label{eq:8}
    f_i(t)=C_iF_i(t)
where $C_i=\begin{bmatrix}

@@

\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:smooth model}) and (\ref{eq:8}) into (\ref{eq:error}), we get:
\begin{equation} \label{eq:9}

@@

        & y(t)=\bar{C}\bar{e}(t)

@@

\textit{
    \begin{remark}

>>>>

\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

@@

\begin{abstract}
In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue (S\&R) usage. The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them. Then we focus on two issues, local motion planning and tracking control. We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot. The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail. By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation. The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure. Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved. Simulations are given ...
\end{abstract}

\begin{keywords}
biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, S\&R, smoothing signal model, UAV, UAVs-UGVs team system
\end{keywords}

@@

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, and surveillance, etc (cite:UV). Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}. However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS). Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.

@@

Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV). Additionally, the complementarity between them also makes such a system more potential. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAVs-UGVs team system will be more appealing. To discuss more concretely, we consider an UAVs-UGVs team system for S\&R. For the need for search mobility, we choose quadrotor aircraft as UAV. In order to deal with the complex terrain of the S\&R environment, we choose biped robot as UGV. Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system.

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose an system architecture of UAVs-robots team system (URTS) for S\&R usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control. It is because the UTRS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a target location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to determine. Then, a local motion corresponding to the behavior of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

% To discuss the local motion planning problem and tracking control problem, the real mechanical system for each agent corresponds must be considered. To meet the need for search mobility, we choose quadrotor aircraft as UAV. The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control). In order to deal with the complex terrain of the S\&R environment, biped robot was chosen as the UGV. Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system. However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved. The local motion planning of the walking of biped robot, i.e., stable walking pattern generation, is discussed in this paper. Related researches can be found in (cite: walking pattern).

@@

\section{PRELIMINARIES OF S\&R URTS}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target. 
% It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

@@

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in S\&R is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=.5]{fig/sys.pdf}\caption{The system architecture of agent in URTS. The 2 blocks on left side are used to convert low-level sensor information into high-level information, such as map, start point and object information. The 5 blocks on right side are the flow of an agent performing a S\&R mission. From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control}%
\label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

@@

\subsection{motion planning of flying of UAV}
A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f \\ \tau
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % form 2
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust. This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction. Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n={flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS. Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command. In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}). Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $d_1(t)$. The nominal system (\ref{eq:agent}) then be rewrited as the following real system:

@@

where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.

@@

where $F_i(t)=\begin{bmatrix}
    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-kh)
\end{bmatrix}^T\in\mathbb{R}^{(k+1)n}$, $A_i\in\mathbb{R}^{{(k+1)n}\times{(k+1)n}}$, $v_i(t)$ is the model error, and $C_i=\begin{bmatrix}

@@

    \end{bmatrix}\otimes I_{n_i}$ with $n_1=n$ and $n_2 = o$. Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get:
\begin{equation} \label{eq:e_bar}

@@

        & y(t)=\bar{C}\bar{e}(t) + C\pmb{r}(t)

@@

%         The equation (\ref{eq:df}) is derived by Taylor expansion, so Assumption \ref{asm:smooth} is nessasry. Unlike previous work, a finite-difference-method-based modeling method is proposed, which reduce the approximation error between origin fault signal and its smooth model. Besides, the fault signals $f_i(t)$ are assumed to be of differentiability class $C^{p-1}$ rather than bounded, which will make the proposed method more general for practical scenario.
Since the fault signals become a state variable of the augment system in (\ref{eq:e_bar}), a Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC:
